\bf Designing Modular Software: A Case Study in Introductory Statistics

### 2016-12-09 jcgs-paper-2016/paper.Rmd
Rebuild with fixed cite

Though challenging in a GUI, a reproducibility framework has three key advantages. First, it eases a student who may be intimidated by programming into the idea that interacting with a user interface is really just a frontend for code. Seeing the correspondence between graphical clicks and printed code should help lessen the fear of coding that many students may have. Second, an analysis created by a reproducible software system can be brought in an R session to easily assess and extend the results. Finally, with the help of knitr [@xie2015] and rmarkdown [@rmarkdown], "printing" the results of a reproducible software system analysis amounts to nothing more than executing the R code on the server, adding another layer of reproducibility. These concepts are important because they encourage best practices with regards to disclosure of analysis methods in research [@baggerly2011reproducible; @xie2015].

>>>>

Though challenging in a GUI, a reproducibility framework has three key advantages. First, it eases a student who may be intimidated by programming into the idea that interacting with a user interface is really just a frontend for code. Seeing the correspondence between graphical clicks and printed code lessens the fear of coding that many students may have. Second, an analysis created by a reproducible software system can be brought in an R session to easily assess and extend the results. Finally, with the help of knitr [@xie2015] and rmarkdown [@rmarkdown], "printing" the results of the analysis amounts to nothing more than executing the R code on the server, adding another layer of reproducibility. These concepts are important because they encourage best practices with regards to disclosure of analysis methods in research [@baggerly2011reproducible; @xie2015].

### 2016-12-09 jcgs-paper-2016/paper.tex
Rebuild with fixed cite

Modern web technologies have enabled a new generation of software
packages that reside solely on the web, which eliminates the issue of
local installation and helps abstract away some of the more challenging
programming aspects of working directly with R. Upon the release of
RStudio's Shiny (RStudio and Inc. 2014) it became easier for an R-based
analysis to be converted to an interactive web application. Several
recent software packages have built upon Shiny to provide a web-based
system based on R. One such package is iNZight Lite (Wild 2015) which
attempts to expose students to data analysis without requiring
programming knowledge. inZight Lite is currently partially but not fully
reproducible. Another package is called Radiant (Nijs 2016), which is a
web-based application with the aim of furthering business education and
financial analysis. While the application is modular and extensible, it
does require local installation and hosting. An overview of the
comparison between the features of these statistical software packages
is presented in Table \ref{tab:compare}. Partial fulfillment of
requirements is noted in the table, as well as a measure of the
complexity of functionality offered by default. For example, \texttt{R}
does have an associated Graphical User Interface (GUI), however this
interface is very limited, thus only partially fulfilling the behavior
of a GUI.

@@

Though challenging in a GUI, a reproducibility framework has three key
advantages. First, it eases a student who may be intimidated by
programming into the idea that interacting with a user interface is
really just a frontend for code. Seeing the correspondence between
graphical clicks and printed code should help lessen the fear of coding
that many students may have. Second, an analysis created by a
reproducible software system can be brought in an R session to easily
assess and extend the results. Finally, with the help of knitr (Xie
2015) and rmarkdown (Allaire et al. 2014), ``printing'' the results of a
reproducible software system analysis amounts to nothing more than
executing the R code on the server, adding another layer of
reproducibility. These concepts are important because they encourage
best practices with regards to disclosure of analysis methods in
research (Baggerly and Berry 2011; Xie 2015).

@@

Shiny observers are a class of reactive objects within the Shiny
paradigm which do not return a value (RStudio and Inc. 2014). For
further discussion of reactivity, see Section
\ref{designing-for-reactivity}. In this example, observers are created
to ensure that the choices of variable for the \texttt{nonparametric}
module are only numeric variables. This is accomplished by utilizing the
global reactive \texttt{intro.numericnames()}, which returns a character
vector containing the variables in the current dataset that are numeric.
Finally, there is an event observer to store code generated from the
module into the overall code script upon clicking the store button. The
presence of this observer code and the definition of the button in the
user interface are enforced, and must be present in any \texttt{intRo}
module.

@@

Reactive programming is a programming paradigm that ``tackles issues
posed by event-driven applications by providing abstractions to express
programs as reactions to external events and having the language
automatically manage the flow of time (by conceptually supporting
simultaneity), and data and computation dependencies'' (Bainomugisha et
al. 2012). As implemented by Shiny, results automatically update when
users interact with the interface.

@@

\hypertarget{ref-bainomugisha2012survey}{}
Bainomugisha, Engineer, Andoni Lombide Carreton, Tom Van Cutsem, Stijn
Mostinckx, and Wolfgang De Meuter. 2012. ``A Survey on Reactive
Programming.'' In \emph{ACM Computing Surveys}. Citeseer.

@@

\hypertarget{ref-parnas1972criteria}{}
Parnas, David Lorge. 1972. ``On the Criteria to Be Used in Decomposing
Systems into Modules.'' \emph{Communications of the ACM} 15 (12). ACm:
1053--8.

@@

\hypertarget{ref-shiny}{}
RStudio, and Inc. 2014. \emph{Shiny: Web Application Framework for R}.
\url{http://CRAN.R-project.org/package=shiny}.

@@

\hypertarget{ref-szyperski1996independently}{}
Szyperski, Clemens. 1996. ``Independently Extensible Systems-Software
Engineering Potential and Challenges.'' \emph{Australian Computer
Science Communications} 18. UNIVERSITY OF CANTERBURY: 203--12.

>>>>

Modern web technologies have enabled a new generation of software
packages that reside solely on the web, which eliminates the issue of
local installation and helps abstract away some of the more challenging
programming aspects of working directly with R. Upon the release of
RStudio's Shiny (RStudio, Inc. 2014) it became easier for an R-based
analysis to be converted to an interactive web application. Several
recent software packages have built upon Shiny to provide a web-based
system based on R. One such package is iNZight Lite (Wild 2015) which
attempts to expose students to data analysis without requiring
programming knowledge. inZight Lite is currently partially but not fully
reproducible. Another package is called Radiant (Nijs 2016), which is a
very promising web-based application with the aim of furthering business
education and financial analysis. While the application is modular and
extensible, it does require local installation and hosting. Radiant is a
business analytics platform with a host of functionality, while
\textbf{intRo} focuses on being a simple and extensible web tool for
learning. An overview of the comparison between the features of these
statistical software packages is presented in Table \ref{tab:compare}.
Partial fulfillment of requirements is noted in the table, as well as a
measure of the complexity of functionality offered by default. For
example, \texttt{R} does have an associated Graphical User Interface
(GUI), however this interface is very limited, thus only partially
fulfilling the behavior of a GUI.

@@

Though challenging in a GUI, a reproducibility framework has three key
advantages. First, it eases a student who may be intimidated by
programming into the idea that interacting with a user interface is
really just a frontend for code. Seeing the correspondence between
graphical clicks and printed code lessens the fear of coding that many
students may have. Second, an analysis created by a reproducible
software system can be brought in an R session to easily assess and
extend the results. Finally, with the help of knitr (Xie 2015) and
rmarkdown (Allaire et al. 2014), ``printing'' the results of the
analysis amounts to nothing more than executing the R code on the
server, adding another layer of reproducibility. These concepts are
important because they encourage best practices with regards to
disclosure of analysis methods in research (Baggerly and Berry 2011; Xie
2015).

@@

Shiny observers are a class of reactive objects within the Shiny
paradigm which do not return a value (RStudio, Inc. 2014). For further
discussion of reactivity, see Section \ref{designing-for-reactivity}. In
this example, observers are created to ensure that the choices of
variable for the \texttt{nonparametric} module are only numeric
variables. This is accomplished by utilizing the global reactive
\texttt{intro.numericnames()}, which returns a character vector
containing the variables in the current dataset that are numeric.
Finally, there is an event observer to store code generated from the
module into the overall code script upon clicking the store button. The
presence of this observer code and the definition of the button in the
user interface are enforced, and must be present in any \texttt{intRo}
module.

@@

Reactive programming is a programming paradigm that ``tackles issues
posed by event-driven applications by providing abstractions to express
programs as reactions to external events and having the language
automatically manage the flow of time (by conceptually supporting
simultaneity), and data and computation dependencies'' (Bainomugisha et
al. 2013). As implemented by Shiny, results automatically update when
users interact with the interface.

@@

\hypertarget{ref-bainomugisha2012survey}{}
Bainomugisha, Engineer, Andoni Lombide Carreton, Tom van Cutsem, Stijn
Mostinckx, and Wolfgang de Meuter. 2013. ``A Survey on Reactive
Programming.'' In \emph{ACM Comput. Surv.}, 45:52:1--52:34. 4. New York,
NY, USA: ACM.

@@

\hypertarget{ref-parnas1972criteria}{}
Parnas, D. L. 1972. ``On the Criteria to Be Used in Decomposing Systems
into Modules.'' \emph{Commun. ACM} 15 (12). New York, NY, USA: ACM:
1053--8.

@@

\hypertarget{ref-shiny}{}
RStudio, Inc. 2014. \emph{Shiny: Web Application Framework for R}.
\url{http://CRAN.R-project.org/package=shiny}.

@@

\hypertarget{ref-szyperski1996independently}{}
Szyperski, Clemens. 1996. ``Independently Extensible Systems-Software
Engineering Potential and Challenges.'' \emph{Australian Computer
Science Communications} 18. University of Cambridge: 203--12.
